Use R to demonstrate that the mean minimizes the sum of the squared deviations from the mean. Accomplish the following steps:
Produce a sample of at least 10 or more different numbers
Produce a simulation following the example from the concepts section
Use your simulation to test a range of numbers smaller and larger than the mean to show that the mean minimizes the sum of the squared deviations from the mean.
Plot your results.
```{r}
scores <- c(1,5,4,3,4,3,4,5,6,7,8,7,6,5,4,5,4,3,2,3,4)
#numbers_to_test <- c(1,2,3,4,mean(scores),5,6,7,8)
numbers_to_test <- c(seq(1,mean(scores),.1), mean(scores), seq(mean(scores),8,.1))
sum_sq_deviations <-c() 
for(i in 1:length(numbers_to_test)) {
  sum_sq_deviations[i] <- sum((scores-numbers_to_test[i])^2)
}
#sum_sq_deviations
plot(sum_sq_deviations)
```
Confidence: 100
```
Write a custom R function for any one of the following descriptive statistics: median, mode, standard deviation, variance. Demonstrate that it produces the same value as the base R function given some set of numbers.
```{r}
#even
a <- c(1,5,4,3,4,3,2,3,4,5,6,7)
sorted_a <- sort(a)
length(a)/2
m1 <- length(a)/2
m2 <- (length(a)/2)+1
sorted_a[m1]
sorted_a[m2]
(sorted_a[m1]+sorted_a[m2])/2

#odd
a <- c(1,5,4,3,4,3,2,3,4,5,6)
sorted_a <- sort(a)
ceiling(length(a)/2)
sorted_a[ceiling(length(a)/2)]
(sorted_a[m1]+sorted_a[m2])/2

my_median <- function(x){
  x_length <- length(x)
  if(x_length %% 2 == 0){
    #even numbers
    sorted_x <- sort(x)
    m1 <- length(x)/2
    m2 <- (length(x)/2)+1
    return((sorted_x[m1]+sorted_x[m2])/2)
  } else {
    sorted_x <- sort(x)
    return(sorted_x[ceiling(length(x)/2)])
  }
}
```

```{r}
# mode
a <- c(1,5,4,3,4,3,2,3,4,5,6,7,8,8,8,8,8,8,8,8,8,8)
b <- table(a)
as.numeric((which(b == max(b))))
my_mode <- function(x){
  b <- table(x)
  as.numeric((which(b == max(b))))
}
my_mode(a)
```

```{r}
# variance
my_variance <- function(x){
  sum( (x-mean(x))^2 ) / (length(x)-1)
}
a <- c(1,5,4,3,4,3,2,3,4,5,6,7,8,8,8,8,8,8,8,8,8,8)
my_variance(a)
var(a)
sum( (a-mean(a))^2 ) / length(a)
sum( (a-mean(a))^2 ) / (length(a)-1)
```
